Partitioning mortality into growth-dependent and growth-independent hazards across 203 tropical tree species

### 2018-08-23 ms/manuscript.Rnw
minor typo
Final changes prior to submission

\title{Partitioning growth-dependent from growth-independent influences on tropical tree mortality}

@@

In order to examine how species differed in hazard functions and to understand the effects of species traits, we used the entire dataset to fit a final model containing all three species traits plus a species random effect to capture inter-specific variation not explained by traits. The increase in predictive accuracy afforded by traits (Fig. \ref{fig2}, compare best model at stage 2 with stage 5) was fairly small relative to including species random effects on each parameter (Fig. \ref{fig2} compare stages 5 and 6), signifying that substantial inter-specific variation in mortality rates remains unexplained.

>>>>

\title{Partitioning mortality into growth-dependent and growth-independent hazards across 203 tropical tree species}

@@

In order to examine how species differed in hazard functions and to understand the effects of species traits, we used the entire dataset to fit a final model containing all three species traits plus a species random effect to capture inter-specific variation not explained by traits. The increase in predictive accuracy afforded by traits (Fig. \ref{fig2}, compare best model at stage 2 with stage 5) was fairly small relative to including species random effects on each parameter (Fig. \ref{fig2}, compare stages 5 and 6), signifying that substantial inter-specific variation in mortality rates remains unexplained.

### 2018-08-23 ms/supplementary.Rnw
Final set of changes
Final changes prior to submission

\title{Partitioning growth-dependent from growth-independent influences on tropical tree mortality}
\author{J.S. Camac, R. Condit, R.G. FitzJohn, L. McCalman, D. Steinberg, M. Westoby, S.J. Wright, D.S. Falster}
\correspondingauthor{Corresponding James S Camac. E-mail: james.camac@gmail.com}

@@

\clearpage
\begin{figure*}[!hb]
\centering
\includegraphics{figures/supp_fig7}
\caption{Pairwise comparison between species' wood density, light demand and maximum dbh. Correlations are pearson correlations}
\label{figS7}
\end{figure*}
\end{document}

>>>>

\title{Partitioning mortality into growth-dependent and growth-independent hazards across 203 tropical tree species}
\author{J.S. Camac, R. Condit, R.G. FitzJohn, L. McCalman, D. Steinberg, M. Westoby, S.J. Wright, D.S. Falster}
\correspondingauthor{Corresponding James S Camac. E-mail: james.camac@gmail.com}

@@

\clearpage
\begin{figure*}[!hb]
\centering
\includegraphics{figures/supp_fig7}
\caption{Pairwise comparison between species' wood density, light demand and maximum dbh. Correlations are pearson correlations}
\label{figS7}
\end{figure*}

\clearpage
\begin{figure*}[!hb]
\centering
\includegraphics[width=0.6\textheight]{figures/supp_fig8.png}
\caption{Relationship between tree size and both diameter increment growth (A) and basal area growth (B)}
\label{figS8}
\end{figure*}

\end{document}
